---
title: "Table 1"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    toc: yes
editor_options:
  chunk_output_type: inline
---
We start by a major category at the top. Example: machine learning. The dependents will be the vectors `minor` and `lesser`.


```{r cache=TRUE}
library(petro.One)

major <- c("machine learning")
minor <- c("reservoir", "production", "logging", "completion", "intervention",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics")
lesser <- c("data", "algorithm")

# the returning data structure is a a list
# the list contains two dataframes: one for the keywords and a second for the papers
prod.li <- join_keywords(major, minor, lesser, get_papers = TRUE, sleep = 3)
prod.li
```

The 6000+ paper results may need to clean up, since some papers could be repeating on each of the subcategories.


## Paper count per discipline
This is a quick summary of how many papers on machine learning were produced.
Again, this number may be misleading because papers could be repeating as there could be papers on machine learning that could be crossing disciplinary boundaries. 

### papers that use the keyword **data**

```{r}
library(ggplot2)
library(dplyr)

keywords <- prod.li$keywords    # get the keywords variable from the list

# data only
keywords %>%
    filter(Var3 == "data") %>%
    ggplot(aes(x=reorder(Var2, paper_count), y=paper_count)) +
   coord_flip()+
geom_bar(stat="identity")
```

### papers that use the keyword **algorithm**

```{r}
# algorithm only
keywords %>%
    filter(Var3 == "algorithm") %>%
    ggplot(aes(x=reorder(Var2, paper_count), y=paper_count)) +
   coord_flip()+
    geom_bar(stat="identity")
```

## Plotting using `magrittr
These yield the same results but using a more compressed approach in terms of commands.
We are using the pipe symbol `%>%` to filter the results from one line of command to the next.

```{r}
library(magrittr)
library(dplyr)

keywords.1 <- prod.df %>% 
    # extract2("keywords") %>%
    `[[`("keywords") %>%
    filter(Var3 == "data")

keywords.1 %>% 
    ggplot(aes(x=reorder(Var2, paper_count), y=paper_count)) +
    coord_flip() +
    geom_bar(stat="identity")
```

```{r}

keywords.2 <- prod.df %>% 
    # extract2("keywords") %>%
    `[[`("keywords") %>%
    filter(Var3 == "algorithm")

keywords.2 %>%
    ggplot(aes(x=reorder(Var2, paper_count), y=paper_count)) +
    coord_flip()+
    geom_bar(stat="identity")
```



replace `well construction`1 by `drilling`

```{r}
# replace `well construction`1 by `drilling`
keywords.2 <- prod.df %>% 
    # extract2("keywords") %>%
    `[[`("keywords") %>%
    filter(Var3 == "algorithm") %>%
    mutate(paper_count = ifelse(Var2 == "well construction",, paper_count))
    # mutate(Var2 = ifelse(Var2 == "well construction", "drilling", Var2))

keywords.2 %>%
    ggplot(aes(x = reorder(Var2, paper_count), y=paper_count)) +
    coord_flip()+
    geom_bar(stat="identity")

```


```{r cache=TRUE}
library(petro.One)


major <- c("machine learning")
discipline <- c("reservoir", "production", "logging", "completion", "intervention",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics")
learning <- c("supervised learning", "unsupervised learning")

by.learning <- join_keywords(major, discipline, learning, get_papers = TRUE, sleep = 3)

```



```{r}
library(petro.One)


major <- c("machine learning")
discipline <- c("reservoir", "production", "logging", "completion", "intervention",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics")
learning <- c("supervised learning", "unsupervised learning")

tech_class <- c("clustering", "classification", "regression")

by.learning <- join_keywords(major, discipline, learning, tech_class,
                             get_papers = TRUE, sleep = 3)

```

## by reference in papers: ML techniques

```{r}
library(petro.One)


major <- c("machine learning")
minor <- c("reservoir", "production", "logging", "completion", "intervention",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics")

ml_technique <- c("SVM", "Support Vector Machine",  "Genetic algorithm", "neural network", 
                  "fuzzy logic", "decision tree", "k-means", "boosting", 
                  "deep learning", "PCA", "principal component analysis",
                  "logistic regression", "kernel density estimation", 
                  "nearest neighbors", "reinforcement learning")

by.ml_technique <- join_keywords(major, minor, ml_technique, get_papers = TRUE, sleep = 3)
by.ml_technique
```

### SVM = Support Vector Machine
Replace the long-SVM by SVM

```{r}
var3.str.1 <- "SVM"
var3.str.2 <- "Support Vector Machine"

not.svm.only <- by.ml_technique %>%
    `[[`("keywords") %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 != var3.str.1 & Var3 != var3.str.2) %>% 
    as.data.frame() %>% 
    print
```


```{r rows.print=25}
var3.str.1 <- "SVM"
var3.str.2 <- "Support Vector Machine"

svm.only <- by.ml_technique %>%
    `[[`("keywords") %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 == var3.str.1 | Var3 == var3.str.2) %>% 
    mutate(Var3 = ifelse(Var3 == var3.str.2, var3.str.1, Var3)) %>% 
    group_by(Var1, Var2, Var3) %>% 
    summarize(paper_count = sum(paper_count)) %>% 
    as.data.frame() %>% 
    print

```

```{r}
# binding both dataframes
keywords.new <- rbind(not.svm.only, svm.only)
keywords.new
```


### PCA

```{r}
var3.str.1 <- "PCA"
var3.str.2 <- "principal component analysis"

not.pca.only <- keywords.new %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 != var3.str.1 & Var3 != var3.str.2) %>%
    as.data.frame() %>% 
    print
```

```{r rows.print=25}
var3.str.1 <- "PCA"
var3.str.2 <- "principal component analysis"

pca.only <- keywords.new %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 == var3.str.1 | Var3 == var3.str.2) %>% 
    mutate(Var3 = ifelse(Var3 == var3.str.2, var3.str.1, Var3)) %>% 
    group_by(Var1, Var2, Var3) %>% 
    summarize(paper_count = sum(paper_count)) %>% 
    as.data.frame() %>% 
    print

```

```{r}
keywords.new.2 <- rbind(not.pca.only, pca.only)
keywords.new.2
```

## add new ML techniques
* naive bayes
* "GPR", " Gaussian Processes Regression",
* "gaussian mixture", "hidden markov"
* "deep learning", "convolutional network", "Boltzman machine",

```{r}
library(petro.One)


major <- c("machine learning")
minor <- c("reservoir", "production", "logging", "completion", "intervention", "workover",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics", "surface facilities")

ml_technique.2 <- c("SVM", "Support Vector Machine", "discriminant analysis", 
                    "logistic regression",
                    "naive bayes", "nearest neighbor",
                     "linear regression", "SVR", "Support Vector Regressor", 
                    "GPR", " Gaussian Processes Regression",
                    "decision tree", "neural network", "neural nets",  
                     "k-means", "c-means", "hierarchical", "gaussian mixture", 
                    "hidden markov",
                    
                    "deep learning", "convolutional network", "Boltzman machine",
                    
                   "Genetic algorithm", "fuzzy logic", "boosting", 
                  "PCA", "principal component analysis",
                  "kernel density estimation", 
                   "reinforcement learning")

by.ml_technique.2 <- join_keywords(major, minor, ml_technique.2, get_papers = TRUE, sleep = 3)
by.ml_technique.2

save(by.ml_technique.2, file = "ml_technique_2.rda")  # just in case
```

```{r}
# load(file = "ml_technique_2.rda") 
load("R:/github-oilgains/petro.One/ml_technique_2.rda")
```



```{r}
by.ml_technique.2$keywords
```


```{r}
library(dplyr)

var3.str.1 <- "SVM"
var3.str.2 <- "Support Vector Machine"

not.svm.only <- by.ml_technique.2 %>%
    `[[`("keywords") %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 != var3.str.1 & Var3 != var3.str.2) %>% 
    as.data.frame() %>% 
    print

var3.str.1 <- "SVM"
var3.str.2 <- "Support Vector Machine"

svm.only <- by.ml_technique.2 %>%
    `[[`("keywords") %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 == var3.str.1 | Var3 == var3.str.2) %>% 
    mutate(Var3 = ifelse(Var3 == var3.str.2, var3.str.1, Var3)) %>% 
    group_by(Var1, Var2, Var3) %>% 
    summarize(paper_count = sum(paper_count)) %>% 
    as.data.frame() %>% 
    print

# binding both dataframes
keywords.new <- rbind(not.svm.only, svm.only)
keywords.new
```


```{r}
var3.str.1 <- "PCA"
var3.str.2 <- "principal component analysis"

not.pca.only <- keywords.new %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 != var3.str.1 & Var3 != var3.str.2) %>%
    as.data.frame() %>% 
    print


pca.only <- keywords.new %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 == var3.str.1 | Var3 == var3.str.2) %>% 
    mutate(Var3 = ifelse(Var3 == var3.str.2, var3.str.1, Var3)) %>% 
    group_by(Var1, Var2, Var3) %>% 
    summarize(paper_count = sum(paper_count)) %>% 
    as.data.frame() %>% 
    print

keywords.new.2 <- rbind(not.pca.only, pca.only)
keywords.new.2

```

```{r}
var3.str.1 <- "neural network"
var3.str.2 <- "neural nets"

not.nnet.only <- keywords.new.2 %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 != var3.str.1 & Var3 != var3.str.2) %>%
    as.data.frame() %>% 
    print


nnet.only <- keywords.new.2 %>%
    select(Var1, Var2, Var3, paper_count) %>% 
    filter(Var3 == var3.str.1 | Var3 == var3.str.2) %>% 
    mutate(Var3 = ifelse(Var3 == var3.str.2, var3.str.1, Var3)) %>% 
    group_by(Var1, Var2, Var3) %>% 
    summarize(paper_count = sum(paper_count)) %>% 
    as.data.frame() %>% 
    print

keywords.new.3 <- rbind(not.nnet.only, nnet.only)
keywords.new.3

```

## 

```{r}
library(petro.One)


major <- c("machine learning")
minor <- c("reservoir", "production", "logging", "completion", "intervention", "workover",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics", "surface facilities")

ml_technique.3 <- c("SVR", "Support Vector Regression", 
                    "GPR", " Gaussian Process Regression"
                  )

by.ml_technique.3 <- join_keywords(major, minor, ml_technique.3, get_papers = TRUE, sleep = 3)
by.ml_technique.3

# save(by.ml_technique.2, file = "ml_technique_2.rda")  # just in case
```



```{r}
library(petro.One)


major <- c("machine learning")
minor <- c("reservoir", "production", "logging", "completion", "intervention", "workover",
           "drilling", "geology", "seismic", "petrophysics", "geophysics", 
           "economics", "surface facilities")

ml_technique.3 <- c("SVR", "Support Vector Regression", 
                    "GPR", " Gaussian Process Regression"
                  )

by.ml_technique.3 <- join_keywords(major, minor, ml_technique.3, get_papers = TRUE, sleep = 3)
by.ml_technique.3

# save(by.ml_technique.2, file = "ml_technique_2.rda")  # just in case
```







